Target for the data

### 2023-02-23 build/code/exploration/data_structure.Rmd
inventory of build code

The file `family_rulers_imputed.dta` is a list of ruler-level observations. These rulers happen to be in chronological order, but they're not lineage-year observations. Yet. How do I get them there?

@@

I did something like that in `RulersToTerritoryYears.R`. Surprisingly, only about one-third of territory-year observation have a corresponding ruler who was alive at the time. But I don't think that should be an issue. I should look at some descriptive stats.

>>>>

The file `family_rulers_imputed.dta` is a list of person-level observations. I turn this into a lineage-year panel of rulers in the same way I did for work: filter for non-missing terr_id. 
This relies on what Matthias told me to do in summer being correct. I should verify that non-rulers in `family_rulers_imputed.dta` have missing terr_id.

Discount the rest of this document. Commit it one more time, then remove it in a housekeeping commit. Also remove `RulersToTerritoryYears.R` in that commit.

This is what I previously thought I had to do (but I think it's unnecessary):

@@

This is implemented in `RulersToTerritoryYears.R`. Surprisingly, only about one-third of territory-year observation have a corresponding ruler who was alive at the time. But I don't think that should be an issue. I should look at some descriptive stats.
